\documentclass[12pt]{article}
\usepackage[a4paper,margin=2.2cm]{geometry}
\usepackage{parskip}
\usepackage{xcolor}
\usepackage{microtype}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.9em}
\linespread{1.35}

\definecolor{stagecolor}{HTML}{6A6A6A}
\newcommand{\stage}[1]{{\itshape\color{stagecolor}#1}}

\pagestyle{empty}

\begin{document}

{\Large\bfseries c0mpute --- Pitch Video Script}\\[0.4em]
{\small Target: $\sim$100 seconds spoken. Cap: 120s. One take. Phone propped, lens-level.}

\vspace{1em}\hrule\vspace{1em}

\stage{[On camera. Phone propped up. Look at the lens, not the screen.]}

\vspace{0.5em}

I'm Leyten. I'm building c0mpute. Solo.

\vspace{0.5em}

\stage{[Beat.]}

\vspace{0.5em}

Easiest way to explain it: torrents, but for AI inference.

Right now, AI runs through three companies. They decide what you're allowed to ask. They log every prompt. They charge whatever they want. Meanwhile gamers, hobbyists, anyone with a half-decent GPU --- that hardware sits idle most of the day.

c0mpute connects those two sides. You open a browser tab to chat. Someone else opens a browser tab to run the model on their GPU. They earn SOL. You get an answer. No accounts. No logs. No install --- on either side.

Every other decentralized compute project needs Docker, CUDA drivers, a rented server. That's an audience of devops engineers. c0mpute runs in a browser through WebGPU, which just shipped in every major browser this year. The unlock is real --- consumer GPUs can run 14-billion-parameter models now. We just needed something where participating doesn't require a CLI.

\vspace{0.4em}

\stage{[Slight shift --- this is the ``why me'' beat.]}

\vspace{0.4em}

I'm building it alone, on purpose. The orchestrator, the browser inference, the worker package, the credit system, the payouts --- one repo, one person. No board telling me to add content moderation. No co-founder I have to talk into things. Every decision so far has been ``what makes this actually work for users and workers.'' That's why it does.

\vspace{0.4em}

c0mpute.ai. One tab away.

\vspace{1.5em}\hrule\vspace{1em}

{\small
\textbf{Recording notes}\\[0.3em]
\stage{Read once out loud before recording --- adjust any phrase that doesn't sound like your normal voice.}\\[0.2em]
\stage{Don't memorize. Glance, read, look up, deliver.}\\[0.2em]
\stage{Phone on a stack of books. Window light from the side, not behind you.}\\[0.2em]
\stage{One take is fine. Sincerity reads better than polish --- judges have watched 500 of these.}
}

\end{document}
